\chapter*{Acknowledgements}

First of all, I would like to thank my supervisor, Professor Minoru Okada. Professor Okada is kind, knowledgeable, and rigorous in scientific attitude. Thank him for giving me an opportunity to study in Japan and let me do wireless power transfer research that I am interested in. He has continued to help me during my three years of study and life. At the same time, I would like to thank Professor Yuichi Hayashi for my research advice and guidance, so that I have a deeper understanding of the weak research environment. With his help, Which greatly improved my research.

Then I would like to thank Associate Professor Takeshi Higashino and Assistant Professor Duong Quang Thang. With their help, they have made me better understand the knowledge of wireless power transfer and wireless communication, and they have helped me overcome the difficulties in professional understanding and helped me complete this topic. Thank them very much. Here, I would also like to thank Assistant Professor Chen Na for her continuous help and encouragement in my studies, so that I have a better understanding of the field of communication.

I would also like to thank the members, staff, and seniors of the Network Systems Laboratory for their companionship in the study and life. We studied together and played together, and established a strong friendship together. Thank you to the international students who have helped me while studying abroad. Thank you for your kindness to me.

Finally, I would like to thank my family for their support of studying abroad, let me choose the knowledge I like, and always provide me with abundant financial support.

Thank you all for your attention!